---
title: "Lab_9"
author: "YangXu"
format:
  html:
    embed-resources: true
---

```{r}
library(microbenchmark)
library(parallel)
```
# Problem 1: Vectorization
#### The following functions can be written to be more efficient without using parallel. Write a faster version of each function and show that \
#### (1) the outputs are the same as the slow version, and \ 
#### (2) your version is faster. \
## 1. This function generates an n x k dataset with all its entries drawn from a Poission distribution with mean lambda.
```{r}
fun1 <- function(n = 100, k = 4, lambda = 4) {
  x <- NULL
  
  for (i in 1:n){
    x <- rbind(x, rpois(k, lambda))    
  }
  
  return(x)
}
```
## Show that fun1alt generates a matrix with the same dimensions as fun1 and that the values inside the two matrices follow similar distributions. Then check the speed of the two functions with the following code:
```{r}
fun1alt <- function(n = 100, k = 4, lambda = 4) {
  x <- matrix( rpois(n*k, lambda) , ncol=4)  
  return(x) 
}
```

#### Compare the speed of the two functions
```{r, message=FALSE}
microbenchmark::microbenchmark(   
  fun1(),   
  fun1alt() 
)
```

#### 2. This function finds the maximum value of each column of a matrix (hint: check out the max.col() function). Show that both functions return the same output for a given input matrix, x. Then check the speed of the two functions.
```{r}
# Data Generating Process (10 x 10,000 matrix)
set.seed(1234)
x <- matrix(rnorm(1e4), nrow=10)

# Find each column's max value
fun2 <- function(x) {
  apply(x, 2, max)
}

fun2alt <- function(x) {
  idx= max.col(t(x))
  x[cbind(idx, 1:4)]
}

# Compare the speed of the two functions
microbenchmark::microbenchmark(   
  fun2(x),   
  fun2alt(x) 
)
```

# Problem 3: Parallelization

#### 1. This function implements a serial version of the bootstrap. Edit this function to parallelize the lapply loop, using whichever method you prefer. Rather than specifying the number of cores to use, use the number given by the ncpus argument, so that we can test it with different numbers of cores later.
```{r}
my_boot <- function(dat, stat, R, ncpus = 1L) {
  
  # Getting the random indices
  n <- nrow(dat)
  idx <- matrix(sample.int(n, n*R, TRUE), nrow=n, ncol=R)
  
  # THIS FUNCTION NEEDS TO BE PARALELLIZED
  # EDIT THIS CODE:
  ans <- parallel::mclapply(seq_len(R), function(i) {
    stat(dat[idx[, i], , drop = FALSE])
  }, mc.cores = ncpus)
  
  # Converting the list into a matrix
  ans <- do.call(rbind, ans)

  return(ans)
}
```
#### 2. Once you have a version of the my_boot() function that runs on multiple cores, check that it provides accurate results by comparing it to a parametric model:
```{r}
# Bootstrap of an OLS
my_stat <- function(d) coef(lm(y ~ x, data=d))

# DATA SIM
set.seed(1)
n <- 500; R <- 1e4

x <- cbind(rnorm(n)); y <- x*5 + rnorm(n)

# Checking if we get something similar as lm
ans0 <- confint(lm(y~x))
ans1 <- my_boot(dat = data.frame(x, y), my_stat, R = R, ncpus = 2L)
t(apply(ans1, 2, quantile, c(.025,.975)))
ans0
```

#### 3. Check whether your version actually goes faster when it’s run on multiple cores (since this might take a little while to run, we’ll use system.time and just run each version once, rather than microbenchmark, which would run each version 100 times, by default):
```{r}
system.time(my_boot(dat = data.frame(x, y), my_stat, R = 4000, ncpus = 1L))
system.time(my_boot(dat = data.frame(x, y), my_stat, R = 4000, ncpus = 2L))
```










